R Notebook

### 2022-02-25 Code/Simulation.Rmd
added babu for time series, qqplot try

```{r}
test_snpar <- function(ar, n) {

@@

# Generate histograms plot
hist_snpar <- ggplot(results) +
             geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
             scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
             facet_grid(~histogram) + 
             theme(legend.position = "none")

hist_snpar
```

@@

# Save the histogram figure
ggsave(filename = "hist_rounded.pdf", plot = hist_rounded, path = "../Manuscript", height = 2.1, width = 6)
```

@@

n_tests = 1000
n = 50

@@

proc.time() - ptm
# could try qqplot for unit interval
# is qqplot close to 45 degree line, otherwise no
```

```{r hist_correlationn}
# Test to show that autocorrelation changes the power of the test
test_correlation <- function(n_tests, ars) {

@@

>>>>

```{r snpar}
test_snpar <- function(ar, n) {

@@

# Generate histograms plot
hist_snpar <- ggplot(results) +
             geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
             scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
             facet_grid(~histogram) + 
             theme(legend.position = "none")
```

@@

# Save the histogram figure
ggsave(filename = "hist_rounded.pdf", plot = hist_rounded, path = "../Manuscript", height = 2.1, width = 6)

qqplot(hist1, runif(100), xlab = "Rounded", ylab = "Uniform", main = "Testing qqplot")
abline(0, 1)
p <- ggplot(results, aes(sample = p_values))
p + stat_qq(distribution = stats::qunif) + geom_abline(intercept = 0, slope = 1) + xlim(0, 1) + ylim(0, 1)
```

@@

n_tests = 100
n = 50

@@

proc.time() - ptm

qqplot(test1$p_values[1:100], runif(100), xlab = "KSGeneral", ylab = "Uniform", main = "Testing qqplot")
abline(0, 1)
# could try qqplot for unit interval
# is qqplot close to 45 degree line, otherwise no
```

```{r hist_correlation}
# Test to show that autocorrelation changes the power of the test
test_correlation <- function(n_tests, ars) {

@@

```{r babu}
ecdf.leftcont <- function (x) {
    x <- sort(x)
    n <- length(x)
    if (n < 1) 
        stop("'x' must have 1 or more non-missing values")
    vals <- unique(x)
    ## making it left continuous!
    rval <- approxfun(vals, cumsum(tabulate(match(x, vals)))/n - 1/n, 
        method = "constant", yleft = 0, yright = 1, f = 1, ties = "ordered")
    class(rval) <- c("ecdf", "stepfun", class(rval))
    assign("nobs", n, envir = environment(rval))
    attr(rval, "call") <- sys.call()
    rval
}

ks.np.babu <- function(x, B = 1000) {
    ## for normal distribution only
    n <- length(x)
    Fn <- ecdf(x)
    Gn <- ecdf.leftcont(x)
    mu <- mean(x); ss <- sd(x)
    Ftheta <- pnorm(x, mu, ss)
    Bn1 <- Fn(x) - Ftheta
    Bn2 <- Gn(x) - Ftheta
    d1 <- abs(Bn1)
    d2 <- abs(Bn2)
    stat <- max(d1, d2)
    stat.b <- double(B)
    for (i in 1:B) {
        x.b <- sample(x, size = n, replace = TRUE)
        Fn.b <- ecdf(x.b)
        Gn.b <- ecdf.leftcont(x.b)
        mu.b <- mean(x.b); ss.b <- sd(x.b)
        ## evaluate at x (not x.b)
        Ftheta.b <- pnorm(x, mu.b, ss.b)
        d1.b <- abs(Fn.b(x) - Ftheta.b - Bn1)
        d2.b <- abs(Gn.b(x) - Ftheta.b - Bn2)
        stat.b[i] <- max(d1.b, d2.b)
    }
    p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
    list(p.value = p.value,
         statistic = stat, stat.b = stat.b)
}
```

```{r babu.ts}
ks.np.babu.ts <- function(x, l, B = 1000) {
  ## for normal distribution only
  n <- length(x)
  Fn <- ecdf(x)
  Gn <- ecdf.leftcont(x)
  mu <- mean(x); ss <- sd(x)
  Ftheta <- pnorm(x, mu, ss)
  Bn1 <- Fn(x) - Ftheta
  Bn2 <- Gn(x) - Ftheta
  d1 <- abs(Bn1)
  d2 <- abs(Bn2)
  stat <- max(d1, d2)
  stat.b <- double(B)
  for (i in 1:B) {
    x.b <- x[nmblk(n, 5)]
    Fn.b <- ecdf(x.b)
    Gn.b <- ecdf.leftcont(x.b)
    mu.b <- mean(x.b); ss.b <- sd(x.b)
    ## evaluate at x (not x.b)
    Ftheta.b <- pnorm(x, mu.b, ss.b)
    d1.b <- abs(Fn.b(x) - Ftheta.b - Bn1)
    d2.b <- abs(Gn.b(x) - Ftheta.b - Bn2)
    stat.b[i] <- max(d1.b, d2.b)
  }
  p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
  list(p.value = p.value,
       statistic = stat, stat.b = stat.b)
}
```

```{r hist_babu}
test_babu <- function(n_tests, n, ar, l) {

  results1 <- double(n_tests)
  results2 <- double(n_tests)
  results3 <- double(n_tests)

    cat(i, " ")

    x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n = n)

    results1[i] <- ks.np.babu.ts(x, l, B = 1000)$p.value
    results2[i] <- blkboot(x, ks_statistic, R = 1000, l)$nmp.value
    results3[i] <- ks.test(x, "pnorm")$p.value

  # Create a master data_frame for p-values
  test <- c(rep("Babu", n_tests), rep("Block", n_tests), rep("Naive", n_tests))
  p_values <- c(results1, results2, results3)
  results <- data_frame(p_values, test)

n_tests = 100
n = 100
l = 10
ar = 0.5

# Create the histograms displaying p-values from each test
results <- suppressWarnings(test_babu(n_tests = n_tests, n = n, ar = ar, l = l))

# Time per test
(proc.time() - ptm)["elapsed"] / n_tests

# Total time
proc.time() - ptm

# Generate histograms plot
hist_babu <- ggplot(results) + 
                geom_histogram(aes(x = p_values, fill = test), boundary = 0, binwidth = 1/20) + 
                scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                facet_grid(~test) +
                theme(legend.position = "none")
hist_babu
```

```{r}
#hist_babu1000
#hist_babu_1000
```
